NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE, PG and PS lipids

### 2017-04-18 Manuscript/manuscript.tex
Add results by Thomas Piggot, reported in http://nmrlipids.blogspot.fi/2017/03/nmrlipids-iv-headgroup-glycerol.html

Comparison between experiments and simulations with CHARMM GUI
parameters for PS lipids in Fig. \ref{HGorderParametersPOPS} suggest that
the model overestimates magnitudes in $\beta$ and g$_3$ order parameters
and forking in $\alpha$.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Order parameters for POPS headgroup and glycerol backbone from simulations with CHARMM GUI parameters and experiments without CaCl$_2$ 
    (DOPS from \cite{browning80} contains 0.1M of NaCl, POPC:POPS mixture from \cite{roux90}).
    Absolute values are shown for experimental data, because signs are not known.
    Simulations values are -S$_{CH}$
  }
  \todo{More simulation data for lipids with different headgroups to be collected}
  \todo{CHARMM GUI simulation contains only counter ions as potassium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.}
  \todo{Experimental signs of the order parameters would highly useful.}
\end{figure}

>>>>

Comparison between experiments and simulations with CHARMM GUI
parameters for PS lipids in Fig. \ref{HGorderParametersPOPS} suggest that
the model overestimates magnitudes in $\beta$ and g$_3$ order parameters
and forking in $\alpha$.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Order parameters for POPS (top) and DOPS (bottom) headgroup and glycerol
    backbone from simulations with different models and experiments without CaCl$_2$ 
    (DOPS from \cite{browning80} contains 0.1M of NaCl, POPC:POPS mixture from \cite{roux90}).
    Absolute values are shown for experimental data, because signs are not known.
    Simulations values are -S$_{CH}$
  }
  \todo{More simulation data for lipids with different headgroups to be collected} \\
  \todo{Some simulations contain potassium as counterions, while some sodium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Experimental signs of the order parameters would highly useful.} \\
  \todo{Why there is difference between CHARMM36 simulation results from POPS:POPC mixture and
  pure POPS?}
\end{figure}
